---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Fernando Rocha"
date: "2024-03-23"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application

Using the data provided by Motor Trend Cars dataset, we fit a linear model evaluate the effect of fuel consumption based on engine power and number of gears and cylinders of the car.

The application is running on (https://n80gm9-fernando-rocha.shinyapps.io/Week4Project/)

ui.R, and Server.R Code in my github repository (https://github.com/fernando-almeida-r/project_week4)

## Motor Trend Cars Dataset

The data used in the app comes from the Motor Trend Cars dataset. 

```{r summary}
data(mtcars)
summary(mtcars)
```

## Plot
In the scatterplot below are represented the data used for the linear model.

```{r plot}

data(mtcars)

plot(jitter(mtcars$mpg) ~ mtcars$hp,
     xlab="Engine Power (HP)",
     ylab="Miles per galon (MPG)",
     main="Effect of Fuel Consumption based on Engine Power",
     pch=19,
     frame.plot=FALSE)

```
